Tools for reproducible ex-post survey data harmonization

### 2020-07-22 data-raw/article.Rmd
citations

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::write_bib(c(
  .packages(), 'haven', 'labelled', 'vctrs', 'retroharmonize'
), 'packages.bib')
```

@@

We introduce the `retroharmonize` and `eurobarometer` packages that help the reproducible, metadata-rich ex-post harmonization of survey data stored in various individual files.  We illustrate the proposed workflow using the case of the Eurobarometer surveys, which provide rich data on European publics in form of single-wave SPSS files from a period of over 25 years. Our tools are flexible and can be applied to other survey projects: we also introduce [a small case study](http://retroharmonize.satellitereport.com/articles/afrobarometer.html) with Afrobarometer.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::write_bib(c(
  .packages(), 'haven', 'labelled', 'vctrs', 'retroharmonize', 'eurobarometer'
), 'packages.bib')
```

@@

We introduce the `retroharmonize` [@R-retroharmonize] and `eurobarometer` [@R-eurobarometer] packages that help the reproducible, metadata-rich ex-post harmonization of survey data stored in various individual files.  We illustrate the proposed workflow using the case of the Eurobarometer surveys, which provide rich data on European publics in form of single-wave SPSS files from a period of over 25 years. Our tools are flexible and can be applied to other survey projects: we also introduce [a small case study](http://retroharmonize.satellitereport.com/articles/afrobarometer.html) with Afrobarometer.
